### 2015-05-15 evaluation.tex
Can you be specific about to whom you filed the bug report?  Ideally, provide a link to a bug tracker.

As an example of the second case, we found the following race in the generic\_nvram char driver (see Figure~\ref{fig:data_race_example} for the source code): during the \texttt{llseek} entry point, the driver is accessing the file offset \texttt{file->f\_pos} without first acquiring a lock (\texttt{file} is passed as a parameter to \texttt{llseek}). This can lead to a race if the driver invokes \texttt{llseek} from another thread passing the same \texttt{file} object as a parameter. When we investigated another char driver that uses the same APIs, we saw that it was protecting the offset access in its \texttt{llseek} entry point with a mutex. This made us suspicious that the race we found in generic\_nvram could be real. We filed a bug report, but did not manage to get a response yet.

>>>>

As an example of the second case, we found the following race in the generic\_nvram char driver (see Figure~\ref{fig:data_race_example}): in the \texttt{llseek} entry point the driver accesses the file offset \texttt{file->f\_pos} without a lock (\texttt{file} is passed as a parameter to \texttt{llseek}). This causes a race if the driver invokes \texttt{llseek} from another thread passing the same \texttt{file} object as a parameter.  We observed that another char driver, using the same APIs, \emph{does} use a mutex to protect the offset access in its \texttt{llseek} entry point, leading us to suspect that the race we found in generic\_nvram is not benign.  We have filed a bug report \ADComment{to whom?} and are awaiting a response.
